Notes on Big MRA

### 2018-05-14 TEX/draft3.tex
updates on section 2

In this section we show numerical results, while leaving the specific details of the experiments for Section~\ref{sec:methods}.
In the first experiment, we estimated Einstein's image from micrographs with $\sigma=3$. An illustrative example for a micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
Multiple occurrences of the image were placed 
in $P$ micrographs, each of of size $4000\times 4000$ pixels, while the images to be separated by the image's length in each direction. From the micrographs, we estimated the first and second order autocorrelation and used a standard phase retrieval algorithm, called relaxed-reflect-reflect, to estimate the image. 
\TODO{We have a movie in the supplementary material.}

As initial guess, we picked an image of the physicist Issac Newton. If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similarly to the ``Einstein from noise'' effect. However, the experiment exhibits the desired phenomenon: the more data we collect, the better the reconstruction quality.
Figure~\ref{fig:Einst_example} demonstrates several recovery results for different number of micrographs collected. Figure~\ref{fig:error_per_micro} presents the normalized recovery error and the power spectrum estimation error as a function of the number of micrographs.
To measure error, we use the root mean square error (RMSE) defined as 
\begin{equation}
\text{RMSE}  = \frac{\|x - \hat{x}\|_{\text{F}}}{\|x \|_{\text{F}}},
\end{equation} 
where $\hat{x}$ is the estimated image and $\|\cdot\|_{\text{F}}$ is the Frobenius norm. 
As expected, the RMSE of estimating the power spectrum (an equivalent quantity to the second-order autocorrelation)  decreases linearly with slope $-1/2$ in logarithmic scale. \TODO{What about the error?}

\begin{figure}[h!]
	\centering
	\begin{subfigure}[h]{0.25\textwidth}
		\centering
		\includegraphics[scale=0.4]{Newton}
		\caption{Newton  (model)}
	\end{subfigure}%
	\begin{subfigure}[h]{0.25\textwidth}
		\centering
		\includegraphics[scale=0.4]{Einstein_100}
		\caption{$P =10^2$}
	\end{subfigure}%
	\begin{subfigure}[h]{0.25\textwidth}
		\centering
		\includegraphics[scale=0.4]{Einstein_1e3}
		\caption{$P =10^3$}
	\end{subfigure}%
	\begin{subfigure}[h]{0.25\textwidth}
		\centering
		\includegraphics[scale=0.4]{Einstein_1e4}
		\caption{$P = 10^4$}
	\end{subfigure}%
	\caption{\label{fig:Einst_example} Recovery of Einstein image. The algorithm is initialized by the image of Newton. We show estimations of Einstein using $P=10^2,10^3$ and $10^4$ number of micrographs, each contains $860$ image occurrences on average. The normalized recovery error is $0.555$, $0.3988$ and $0.2907$, respectively. The normalized error in recovering the power spectrum was $69.1\times10^{-3} $, $21.7\times10^{-3} $ and $6.8\times10^{-3}$, respectively. \TODO{This image will be more impressive in the future}}	
\end{figure}

Results from a similar experiment for 1-D signals is presented in Figures~\ref{fig:1Dhomosignals} and~\ref{fig:1DhomoRMSE}.
Here, we used nonconvex least-squares (LS) to estimate the signal and the estimated number of its occurrences.
We do not assume the knowledge of the noise level. 
Crucially, starting from the point of $n\approx10^8$, the RMSE of the signal estimation decreases linearly with slope $-1/2$---the expected estimation rate of the autocorrelation functions---implying the stability of the recovery algorithm. \TODO{We may want to replace with an experiment with colored noise}

\begin{figure}[h!]
	\centering
	\begin{subfigure}[h]{0.5\textwidth}
		\centering
		\includegraphics[scale=0.6]{err_rrr_per_micrograph}
		\caption{}	
	\end{subfigure}%
	\begin{subfigure}[h]{0.5\textwidth}
		\centering
		\includegraphics[scale=0.6]{err_PS_per_micrograph}
		\caption{}	
	\end{subfigure}%
	\caption{\label{fig:error_per_micro} The left panel shows the recovery error (in log-log scale) of Einstein's image defined in~\eqref{eq:error} as a function of the number of the collected micrographs. The right panel presents the error of estimating the power spectrum of the signal from the data. As expected, in log-log scale, the curve has a $-1/2$ slope.}	
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[scale=0.45]{progressive_n}
	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
	\label{fig:1Dhomosignals}
\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=0.5\linewidth]{XP_1D_homogeneous_new_ROI/progressive_RMSE_n}
	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
	\label{fig:1DhomoRMSE}
\end{figure}

Figure~\ref{fig:1Dheterosignals} demonstrates accurate estimation of three signals simultaneously with noise level $\sigma=3$. We define the ratio of the space occupied by the $i$th signal as 
\begin{equation}
\gamma_i = \frac{M_i L}{N},
\end{equation}
where $M_i$ is the signal's number of occurrences, $L$ is the length of the signal and $N$ is the micrograph length. In the experiment, we do not assume to know these ratios, neither the noise level $\sigma$. As can be seen, given enough signals occurrences, we can estimate accurately the signals. he estimation quality 
is poorer than the other two signals, a phenomenon that can be explained using Proposition~\ref{prop:uniqueness}.

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{XP_1D_heterogeneous/hetero_example}
	\caption{Red signals are the ground truth (targets) and the blue signals are our estimations. Individual RMSE of the estimates: $0.0239393 / 0.208925 / 0.0335956$. The estimated $\gamma$'s are $0.02574 / 0.01693 / 0.00818$ and the true ones $0.02561 / 0.01707 / 0.00853$. The $\SNR$ is $1/12$.}
	\label{fig:1Dheterosignals}
\end{figure}

>>>>

In this section we describe  some numerical experiments and show results. The experimental details are discussed at length in Section~\ref{sec:methods}.
In the first experiment, we estimated Einstein's image of size $50\times 50$ from multiple micrographs of size $4096\times 4096$ pixels, contaminated  with additive i.i.d.\ Gaussian noise with standard deviation $\sigma=3$. An illustrative example of a micrograph appears in the right panel of Figure~\ref{fig:micro_example}.
In each micrograph, multiple occurrences of the Einstein's image    were placed, while keeping a separation of  $50$ pixels between the images in each direction. From the micrographs, we estimated the power spectrum, which is equivalent to the second-order autocorrelation. Then, in order to estimate the signal itself, we applied a standard phase retrieval algorithm, called relaxed-reflect-reflect.

As initial guess, we picked an image of the physicist Issac Newton. If the algorithm was prone to model bias, we would expect to get as an output an image that resembles Newton, similarly to the ``Einstein from noise'' effect. However, the experiment exhibits the desired phenomenon: the more data we collect, the better the reconstruction quality.
Figure~\ref{fig:Einst_example} demonstrates several recovery results for different number of micrographs collected. Figure~\ref{fig:error_per_micro} presents the normalized recovery error and the power spectrum estimation error as a function of the number of micrographs.
To measure the error, we use the root mean square error (RMSE) defined as 
\begin{equation}
\text{RMSE}  = \frac{\|x - \hat{x}\|_{\text{F}}}{\|x \|_{\text{F}}},
\end{equation} 
where $\hat{x}$ is the estimated image and $\|\cdot\|_{\text{F}}$ stands for the Frobenius norm. 
As expected, the RMSE of estimating the power spectrum   decreases linearly with slope $-1/2$ in logarithmic scale. 
\TODO{Few comments: 1. We have a movie in the supplementary material. 2. Does the error also have the right slope? 3. We can put more images to exemplify the progress 4. Need to improve the micrograph's generation code  }

\begin{figure}[h!]
	\centering
	\begin{subfigure}[h]{0.25\textwidth}
		\centering
		\includegraphics[scale=0.3]{Newton}
		\caption{Newton  (model)}
	\end{subfigure}%
	\begin{subfigure}[h]{0.25\textwidth}
		\centering
		\includegraphics[scale=0.3]{reconstruction2}
		\caption{$P = 1024$}
	\end{subfigure}%
	\begin{subfigure}[h]{0.25\textwidth}
		\centering
		\includegraphics[scale=0.3]{reconstruction20}
		\caption{$P = 1024\times 10$}
	\end{subfigure}%
	\begin{subfigure}[h]{0.25\textwidth}
		\centering
		\includegraphics[scale=0.3]{reconstruction200}
		\caption{$P = 1024\times 100$}
	\end{subfigure}%
	\caption{\label{fig:Einst_example} Recovery of Einstein image. The algorithm is initialized by the image of Newton. We show estimations of Einstein using $P=1024,1024\times 10$ and $1024\times 100$ number of micrographs, each contains $800$ image occurrences on average (to verify). The normalized recovery error is $0.5514$, $0.3494$ and $0.2112$, respectively. The normalized error in recovering the power spectrum was $0.0269 $, $0.0083$ and $0.0027$, respectively. }	
\end{figure}

%
%Figure~\ref{fig:1Dheterosignals} demonstrates accurate estimation of three signals simultaneously with noise level $\sigma=3$. We define the ratio of the space occupied by the $i$th signal as 
%\begin{equation}
%\gamma_i = \frac{M_i L}{N},
%\end{equation}
%where $M_i$ is the signal's number of occurrences, $L$ is the length of the signal and $N$ is the micrograph length. In the experiment, we do not assume to know these ratios, neither the noise level $\sigma$. As can be seen, given enough signals occurrences, we can estimate accurately the signals. he estimation quality 
%is poorer than the other two signals, a phenomenon that can be explained using Proposition~\ref{prop:uniqueness}.

Results from a similar experiment  with $\sigma=3$ for $K=3$ 1-D signals is presented in Figures~\ref{fig:1Dheterosignals}.
 We define the ratio of the space occupied by the $i$th signal as 
\begin{equation}
\gamma_i = \frac{M_i L}{N},
\end{equation}
where $M_i$ is the signal's number of occurrences, $L$ is the length of the signal and $N$ is the micrograph length.
In the experiment, we do not assume to know these ratios, neither the noise level $\sigma$. 
We used nonconvex least-squares (LS) to estimate the signals and the estimated number of their occurrences.
As can be seen, given enough signals occurrences, we can estimate accurately the signals. he estimation quality 
is poorer than the other two signals, a phenomenon that can be explained using Proposition~\ref{prop:uniqueness}.
\TODO{We will replace the figure with a ``progress figure'' (like we did for Einstien) for each signals and a plot of the recovery error.}
%We do not assume the knowledge of the noise level. 
%Crucially, starting from the point of $n\approx10^8$, the RMSE of the signal estimation decreases linearly with slope $-1/2$---the expected estimation rate of the autocorrelation functions---implying the stability of the recovery algorithm.

\begin{figure}[h]
\centering
\includegraphics[scale=.5]{Einstein_progress}
\caption{\label{fig:error_per_micro} The left panel shows the recovery error (in log-log scale) of Einstein's image defined in~\eqref{eq:error} as a function of the number of the collected micrographs. The right panel presents the error of estimating the power spectrum of the signal from the data. As expected, in log-log scale, the curve has a $-1/2$ slope.}	
\end{figure}

%
%\begin{figure}[t]
%	\centering
%	\includegraphics[scale=0.45]{progressive_n}
%	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
%	\label{fig:1Dhomosignals}
%\end{figure}
%
%\begin{figure}[t]
%	\centering
%	\includegraphics[width=0.5\linewidth]{XP_1D_homogeneous_new_ROI/progressive_RMSE_n}
%	\caption{\TODO{...} \TODO{This figure is with new ROI method based on loss functions}}
%	\label{fig:1DhomoRMSE}
%\end{figure}

\begin{figure}[t]
	\centering
	\includegraphics[width=\linewidth]{XP_1D_heterogeneous/hetero_example}
	\caption{Red signals are the ground truth (targets) and the blue signals are our estimations. Individual RMSE of the estimates: $0.0239393 / 0.208925 / 0.0335956$. The estimated $\gamma$'s are $0.02574 / 0.01693 / 0.00818$ and the true ones $0.02561 / 0.01707 / 0.00853$. The $\SNR$ is $1/12$. \TODO{to replace with a progress plot`}}
	\label{fig:1Dheterosignals}
\end{figure}

### 2018-05-14 TEX/notes_will/notes_moments/backups/test1_save1.tex
updates on section 2

We have the following model. $x$ is a signal of length $L$. For large $n$, we observe the vector $Y$, which is of the form 
%
\begin{align}
%
    Y = x \ast g + \ep
%
\end{align}
%
where $g$ is a sum of diracs at locations at least $L$ apart, and $\ep$ is a vector of $n$ iid Gaussians. The question is, can we recover $x$?

@@

\section{Pure noise}

The first step is to analyze the pure noise case.

TKTK

\section{Signal plus noise}

>>>>

We have the following model. $x$ is a signal of length $L$. For large $n$, we observe the vector $Y \in \mathbb{R}^n$, which is of the form 
%
\begin{align}
%
    Y = x \ast g + \ep
%
\end{align}
%
where $g$ is a sum of diracs at locations at least $L$ apart, and $\ep$ is a vector of $n$ iid Gaussians. The question is, can we recover $x$?

@@

Note that I'm not just computing the expected value. I'm actually showing convergence almost surely as $n \to \infty$.

\section{First moment}

We'll compute the limiting vector of the average of all the windows. Fix an index $\ell$ between $1$ and $L$. Then

\section{Second moment}

\subsection{Pure noise}

\subsection{Signal plus noise}

### 2018-05-14 TEX/notes_will/notes_moments/backups/test1_save2.tex
updates on section 2

The approach Tamir proposed was the following. Look at all length $L$ (or bigger, but we'll stick with length $L$ for now) subvectors of $Y$ (with consecutive elements). Compute the mean, power spectrum, and bispectrum for each, and average. This should hopefully converge in the large $n$ limit to some function of $x$. Then attempt to invert this function, perhaps by least squares.

@@

@@

We'll compute the limiting vector of the average of all the windows. Fix an index $\ell$ between $1$ and $L$. Then

@@

Assume that the first and last copies of $x$ is at least $L$ places removed from the boundaries of the interval $[1,n]$ (if not we can just zero-pad the interval).

>>>>

The approach Tamir proposed was the following. We look at all length $L$ subvectors of $Y$ (with consecutive elements). Compute the mean, power spectrum, and bispectrum for each, and average. This should hopefully converge in the large $n$ limit to some function of $x$. Then attempt to invert this function, perhaps by least squares.

@@

We will assume that the first and last copies of $x$ is at least $L$ places removed from the boundaries of the interval $[1,n + L]$ (if not we can just zero-pad the interval). We will also denote by $I_1,\dots,I_J$ the $J$ subintervals containing the signal; and take $I_j = [a_j,b_j]$. When we take the limit $n \to \infty$, we'll let $J = J_n$ grow with $n$, as is natural. We will see that we require $J_n = \Omega(n)$ in order for the limits to not vanish.

@@

We'll compute the limiting vector of the sample average of all the windows. We fix an index $\ell$ between $1$ and $L$. Then the sample average of the $\ell^{th}$ entry is:
%
\begin{align}
%
    \frac{1}{n} \sum_{i=1}^n Y_{i+\ell} &=
    \frac{1}{n}  \left( \sum_{i \notin I_j \forall j} \ep_i 
                  + \sum_{j=1}^J \sum_{k=1}^L (x[k] + \ep_{a_j + k-1} ) \right) 
    \nonumber \\
%
                &= \frac{1}{n}\sum_{i=1}^{n} \ep_i 
                  + \frac{J \cdot L}{n} \left(\frac{1}{L} \sum_{k=1}^L x[k]\right) 
    \nonumber \\
                &= \frac{1}{n}\sum_{i=1}^{n-L+1} \ep_i 
                  + \frac{J \cdot L}{n} \bar{x}       \nonumber \\
%
                &\operatorname*{\longrightarrow}^{a.s.}  \gamma  \cdot L \cdot \bar{x}
%
\end{align}
%
where $\gamma = \lim_{n\to\infty} J_n / n$. This limit does not depend on the index $\ell$, and is the same limit as if there were no noise at all, i.e.\ the noise completely averages out.

Actually, what Tamir meant when he said first moment was the average of the windows' averages. But this also converges a.s.\ to $\gamma \cdot L \cdot \bar{x}$, by simply exchanging limits and finite sums, as follows. The sample mean of the window starting at index $i$ is just $\frac{1}{L} \sum_{k=0}^{L-1} Y_{i+k}$. Averaging these over all $n$ windows and taking the limit as $n \to \infty$ we get:
%
\begin{align}
%
    \lim_{n\to\infty} \frac{1}{n} \sum_{i=1}^n \frac{1}{L} \sum_{k=0}^{L-1} Y_{i+k}
    =  \frac{1}{L} \sum_{k=0}^{L-1} \lim_{n\to\infty} \frac{1}{n} \sum_{i=1}^n Y_{i+k}
    = \gamma \cdot L \cdot \bar{x}.
%
\end{align}

@@

### 2018-05-14 TEX/notes_will/notes_moments/backups/test1_save3.tex
updates on section 2

We'll compute the limiting vector of the sample average of all the windows. We fix an index $\ell$ between $1$ and $L$. Then the sample average of the $\ell^{th}$ entry is:
%
\begin{align}
%
    \frac{1}{n} \sum_{i=1}^n Y_{i+\ell} &=
    \frac{1}{n}  \left( \sum_{i \notin I_j \forall j} \ep_i 
                  + \sum_{j=1}^J \sum_{k=1}^L (x[k] + \ep_{a_j + k-1} ) \right) 
    \nonumber \\
%
                &= \frac{1}{n}\sum_{i=1}^{n} \ep_i 
                  + \frac{J \cdot L}{n} \left(\frac{1}{L} \sum_{k=1}^L x[k]\right) 
    \nonumber \\
                &= \frac{1}{n}\sum_{i=1}^{n-L+1} \ep_i 
                  + \frac{J \cdot L}{n} \bar{x}       \nonumber \\
%
                &\operatorname*{\longrightarrow}^{a.s.}  \gamma  \cdot L \cdot \bar{x}
%
\end{align}
%
where $\gamma = \lim_{n\to\infty} J_n / n$. This limit does not depend on the index $\ell$, and is the same limit as if there were no noise at all, i.e.\ the noise completely averages out.

Actually, what Tamir meant when he said first moment was the average of the windows' averages. But this also converges a.s.\ to $\gamma \cdot L \cdot \bar{x}$, by simply exchanging limits and finite sums, as follows. The sample mean of the window starting at index $i$ is just $\frac{1}{L} \sum_{k=0}^{L-1} Y_{i+k}$. Averaging these over all $n$ windows and taking the limit as $n \to \infty$ we get:
%
\begin{align}
%
    \lim_{n\to\infty} \frac{1}{n} \sum_{i=1}^n \frac{1}{L} \sum_{k=0}^{L-1} Y_{i+k}
    =  \frac{1}{L} \sum_{k=0}^{L-1} \lim_{n\to\infty} \frac{1}{n} \sum_{i=1}^n Y_{i+k}
    = \gamma \cdot L \cdot \bar{x}.
%
\end{align}

>>>>

We'll compute the limiting vector of the sample average of all the windows. We fix an index $\ell$ between $1$ and $L$. Then the sample average of the $\ell^{th}$ entry is:
%
\begin{align}
%
    \frac{1}{n} \sum_{i=1}^n Y_{i+\ell} &=
    \frac{1}{n}  \left( \sum_{i \notin I_j \forall j} \ep_i 
                  + \sum_{j=1}^J \sum_{k=1}^L (x[k] + \ep_{a_j + k-1} ) \right) 
    \nonumber \\
%
                &= \frac{1}{n}\sum_{i=1}^{n} \ep_i 
                  + \frac{J \cdot L}{n} \left(\frac{1}{L} \sum_{k=1}^L x[k]\right) 
    \nonumber \\
                &= \frac{1}{n}\sum_{i=1}^{n-L+1} \ep_i 
                  + \frac{J \cdot L}{n} \bar{x}       \nonumber \\
%
                &\operatorname*{\longrightarrow}^{a.s.}  \gamma  \cdot \bar{x}
%
\end{align}
%
where $\gamma = \lim_{n\to\infty} J_n L / n$; $\gamma$ is the fraction of the observations occupied by the signal. The limit of the $\ell^{th}$ entry of the mean does not depend on the index $\ell$, and is the same limit as if there were no noise at all, i.e.\ the noise completely averages out.

Actually, what Tamir meant when he said first moment was the average of the windows' averages (a scalar), not the average window (a vector). But this also converges a.s.\ to $\gamma \cdot \bar{x}$, by simply exchanging limits and finite sums, as follows. The sample mean of the window starting at index $i$ is just $\frac{1}{L} \sum_{k=0}^{L-1} Y_{i+k}$. Averaging these over all $n$ windows and taking the limit as $n \to \infty$ we get:
%
\begin{align}
%
    \lim_{n\to\infty} \frac{1}{n} \sum_{i=1}^n \frac{1}{L} \sum_{k=0}^{L-1} Y_{i+k}
    =  \frac{1}{L} \sum_{k=0}^{L-1} \lim_{n\to\infty} \frac{1}{n} \sum_{i=1}^n Y_{i+k}
    = \gamma \cdot \bar{x}.
%
\end{align}

### 2018-05-14 TEX/notes_will/notes_moments/backups/test1_save5.tex
updates on section 2

We'll compute the limiting vector of the sample average of all the windows. We fix an index $\ell$ between $1$ and $L$. Then the sample average of the $\ell^{th}$ entry is:
%
\begin{align}
%
    \frac{1}{n} \sum_{i=1}^n Y_{i+\ell} &=
    \frac{1}{n}  \left( \sum_{i \notin I_j \forall j} \ep_i 
                  + \sum_{j=1}^J \sum_{k=1}^L (x[k] + \ep_{a_j + k-1} ) \right) 
    \nonumber \\
%
        &= \frac{1}{n}\sum_{i=1}^{n} \ep_i 
                  + \frac{J \cdot L}{n} \left(\frac{1}{L} \sum_{k=1}^L x[k]\right) 
    \nonumber \\
        &= \frac{1}{n}\sum_{i=1}^{n-L+1} \ep_i 
                  + \frac{J \cdot L}{n} \bar{x}       
     \nonumber \\
%
        &\operatorname*{\longrightarrow}^{a.s.}  \gamma  \cdot \bar{x}
%
\end{align}
%
where $\gamma = \lim_{n\to\infty} J_n L / n$; $\gamma$ is the fraction of the observations occupied by the signal. The limit of the $\ell^{th}$ entry of the mean does not depend on the index $\ell$, and is the same limit as if there were no noise at all, i.e.\ the noise completely averages out.

@@

\subsection{Pure noise}

\subsection{Signal plus noise}

>>>>

We'll compute the limiting vector of the sample average of all the windows. We fix an index $\ell$ between $1$ and $L$. The $\ell^{th}$ entry of the $i^{th}$ window is $Y_{i+\ell-1}$, $i=1,\dots,n$. Then the sample average of the $\ell^{th}$ entry is:
%
\begin{align}
%
    \frac{1}{n} \sum_{i=1}^n Y_{i+\ell - 1} &=
    \frac{1}{n}  \left( \sum_{i \notin I_j \forall j} \ep_i 
                  + \sum_{j=1}^J \sum_{k=1}^L (x[k] + \ep_{a_j + k-1} ) \right) 
    \nonumber \\
%
        &= \frac{1}{n}\sum_{i=1}^{n} \ep_i 
                  + \frac{J \cdot L}{n} \left(\frac{1}{L} \sum_{k=1}^L x[k]\right) 
    \nonumber \\
        &= \frac{1}{n}\sum_{i=1}^{n-L+1} \ep_i 
                  + \frac{J \cdot L}{n} \bar{x}       
     \nonumber \\
%
        &\operatorname*{\longrightarrow}^{a.s.}  \gamma  \cdot \bar{x}
%
\end{align}
%
where $\gamma = \lim_{n\to\infty} J_n L / n$; $\gamma$ is the fraction of the observations containing the signal. The limit of the $\ell^{th}$ entry of the mean does not depend on the index $\ell$, and is the same limit as if there were no noise at all, i.e.\ the noise completely averages out.

@@

First we'll compute the limit in the case of pure noise; then we'll use this for signal plus noise.

\subsection{Second moment of noise}

Here, $Y_i = \ep_i$. We fix two indices $k$ and $l$, and we suppose $k < l$. We will let $\Delta = l-k > 0$. We want to compute the limit $\frac{1}{n} \sum_{i=1}^n Y_{i + k - 1} Y_{i + l - 1} = \frac{1}{n} \sum_{i=1}^n Y_{i + k - 1} Y_{i + k + \Delta - 1}$. Break up the sum into $\Delta$ terms as follows:
%
\begin{align}
%
    \frac{1}{n} \sum_{i=1}^n Y[i + k - 1] & Y[i + k+\Delta - 1]   
    \nonumber \\
    &= \frac{1}{\Delta} \sum_{m=0}^{\Delta-1} \frac{1}{n/\Delta}\sum_{j=1}^{n/\Delta} 
                      Y[j\Delta + m] Y[(j + 1)\Delta + m].
%
\end{align}
%
Each term
%
\begin{math}
    \frac{1}{n/\Delta}\sum_{j=1}^{n/\Delta} 
                      Y[j\Delta + m] Y[(j + 1)\Delta + m]
\end{math}
%
is an average of $n / \Delta$ iid terms with expectation zero, and so converges to 0 a.s.\ as $n \to \infty$.

\subsection{Second moment of signal plus noise}

### 2018-05-14 TEX/notes_will/notes_moments/backups/test1_save6.tex
updates on section 2

\newcommand{\F}{\mathcal{F}}
\newcommand{\ep}{\varepsilon}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\GCD}{\mathbf{GCD}}

@@

Here, $Y_i = \ep_i$. We fix two indices $k$ and $l$, and we suppose $k < l$. We will let $\Delta = l-k > 0$. We want to compute the limit $\frac{1}{n} \sum_{i=1}^n Y_{i + k - 1} Y_{i + l - 1} = \frac{1}{n} \sum_{i=1}^n Y_{i + k - 1} Y_{i + k + \Delta - 1}$. Break up the sum into $\Delta$ terms as follows:
%
\begin{align}
%
    \frac{1}{n} \sum_{i=1}^n Y[i + k - 1] & Y[i + k+\Delta - 1]   
    \nonumber \\
    &= \frac{1}{\Delta} \sum_{m=0}^{\Delta-1} \frac{1}{n/\Delta}\sum_{j=1}^{n/\Delta} 
                      Y[j\Delta + m] Y[(j + 1)\Delta + m].
%
\end{align}
%
Each term
%
\begin{math}
    \frac{1}{n/\Delta}\sum_{j=1}^{n/\Delta} 
                      Y[j\Delta + m] Y[(j + 1)\Delta + m]
\end{math}
%
is an average of $n / \Delta$ iid terms with expectation zero, and so converges to 0 a.s.\ as $n \to \infty$.

@@

>>>>

\newcommand{\F}{\mathcal{F}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\ep}{\varepsilon}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\GCD}{\mathbf{GCD}}

\newcommand{\mean}[2]{\frac{1}{#1}\sum_{#2=1}^{#1}}

@@

Here, $Y_i = \ep_i$. We fix two indices $k$ and $l$, and we suppose $k < l$. We will let $\Delta = l-k > 0$. We want to compute the limit $\frac{1}{n} \sum_{i=1}^n Y_{i + k - 1} Y_{i + l - 1} = \frac{1}{n} \sum_{i=1}^n Y_{i + k - 1} Y_{i + k + \Delta - 1}$. Break up the sum into $\Delta$ terms as follows:
%
\begin{align}
%
    &\frac{1}{n} \sum_{i=1}^n Y[i + k - 1]  Y[i + k+\Delta - 1]   
    \nonumber \\
    =& \frac{1}{\Delta} \sum_{m=0}^{\Delta-1} \frac{1}{n/\Delta}\sum_{j=1}^{n/\Delta} 
                      Y[j\Delta + m] Y[(j + 1)\Delta + m].
%
\end{align}
%
Each term
%
\begin{math}
    \frac{1}{n/\Delta}\sum_{j=1}^{n/\Delta} 
                      Y[j\Delta + m] Y[(j + 1)\Delta + m]
\end{math}
%
is an average of $n / \Delta$ iid terms with expectation zero, and so converges to 0 a.s.\ as $n \to \infty$. (Of course, it's not exactly $n / \Delta$ terms; there will be finitely many terms unaccounted for this way, but these are negligible).

If $k = l$, then it's even easier:
%
\begin{align}
%
    \frac{1}{n} \sum_{i=1}^n Y[i + k - 1]^2 \operatorname*{\longrightarrow}^{a.s.} \sigma^2.
%
\end{align}

So the second moment matrix of pure noise converges a.s.\ as $n \to \infty$ to $\sigma^2 I_L$.

@@

Break the sum $\sum_{i=1}^n Y[i + k-1] Y[i + l - 1]$ into three terms: where $i + k-1$ and $i+l-1$ are disjoint from all intervals $I_j$ -- we will denote this set $\I$; where both $i + k - 1$ and $i + l -1$ lie entirely inside one of the $I_j$; and the rest, where exactly one of $i+k-1$ and $i+l-1$ lie in an interval $I_j$. So we have:
%
\begin{align}
%
    & \sum_{i=1}^n Y[i+k-1] Y[i+l-1]    \nonumber \\
    =& \left(\sum_{i \in \I}  
        + \sum_{j=1}^J \sum_{i=a_j - l + 1}^{a_j - k} 
        + \sum_{j=1}^J \sum_{i=b_j - l + 2}^{b_j - k+1} 
        + \sum_{j=1}^J \sum_{i=a_j-k+1}^{b_j-l+1}
      \right)  Y[i+k-1] Y[i+l-1]
%
\end{align}
We will use that $Y[a_j + m] = x[m+1] + \ep[a_j+m]$, $m=0,\dots,L-1$.

For the second term, the inner sum is
%
\begin{align}
%
    &\sum_{i=a_j - l + 1}^{a_j - k} Y[i+k-1] Y[i+l-1]    \nonumber \\
    =& \sum_{i=a_j - l + 1}^{a_j - k} \ep[i+k-l] (x[i+l-1] + \ep[i+l-1])
    \nonumber \\
    =& \sum_{i=a_j - l + 1}^{a_j - k} \ep[i+k-l] x[i+l-1] 
        + \sum_{i=a_j - l + 1}^{a_j - k} \ep[i+k-l]\ep[i+l-1]
%
\end{align}
%

### 2018-05-14 TEX/notes_will/notes_moments/backups/test2_save1.tex
updates on section 2

The approach Tamir proposed was the following. We look at all length $L$ subvectors of $Y$ (with consecutive elements). Compute the mean, power spectrum, and bispectrum for each, and average. This should hopefully converge in the large $n$ limit to some function of $x$. Then attempt to invert this function, perhaps by least squares.

One of Tamir's concerns is that the noise terms are not independent between overlapping windows. I'll show that at least for the first and second moments, things are okay as long as there are $\Omega(n)$ copies of $x$ buried in $Y$. The bispectrum is probably fine too but I haven't written it out yet.

@@

@@

@@

@@

First we'll compute the limit in the case of pure noise; then we'll use this for signal plus noise.

\subsection{Second moment of noise}

>>>>

@@

%
%
%

@@

\begin{comment}

@@

\end{comment}

%
%
%

@@

We fix a value $\Delta$ between $1$ and $L-1$. We will compute the second moment:
%
\begin{align}
%
    M_2(\Delta) = 
        \lim_{n \to \infty} \frac{1}{n} \sum_{i=1}^{n-\Delta} Y_i Y_{i+\Delta}.
%
\end{align}

First, if there is no noise, and under the wide spacing assumption, we can break the sum into $J_n$ different sums, one for each copy of $x$ embedded in the signal:
%
\begin{align}
%
    M_2(\Delta) 
        = \frac{1}{n} \sum_{j=1}^{J_n} \sum_{i=a_j}^{b_j-\Delta} Y_i Y_{i+\Delta}
    = \frac{1}{n} \sum_{j=1}^{J_n} \sum_{i=1}^{L-\Delta} X_i X_{i+\Delta}
%
\end{align}
